---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all(".")
```

# astimeseries

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Reckziegel/astimeseries.svg?branch=master)](https://travis-ci.org/Reckziegel/astimeseries)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/Reckziegel/astimeseries?branch=master&svg=true)](https://ci.appveyor.com/project/Reckziegel/astimeseries)
[![Codecov test coverage](https://codecov.io/gh/Reckziegel/astimeseries/branch/master/graph/badge.svg)](https://codecov.io/gh/Reckziegel/astimeseries?branch=master)
<!-- badges: end -->

The objective of `astimeseries` is to simplify and assure the correct coercion among data structures used in the `tidyverse` to R-Mertrics (`timeSeries` class). 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("Reckziegel/astimeseries")
```
## Example

Suppose you have the following `tibble`:

```{r example}

library(tibble)

tbl <- tibble(date = as.Date(c('2019-01-01', '2019-01-02', '2019-01-03')),
               a    = rnorm(3),
               b    = rnorm(3),
               c    = rnorm(3))

tbl

```

If you try to coerce the `tbl` object to a `timeSeries` (the data structure R-Metrics likes to work with), the timestamps attributes are lost:

```{r}

library(timeSeries)

as.timeSeries(tbl)
```

Instead, it's safer to use `as_timeseries` to ensure all information is keeped approprietly. 

```{r}
# library(astimeseries)
as_timeseries(tbl)
```

